CUNY SPSS Data Science Math Homework 3

### 2018-07-24 data-science-math/Homework 3.Rmd
More work on homework 3

```{r}
m <- 13000 
sd <- 40000**(1/2)
round(1-pnorm(979, m, sd), 4)
```

@@

```{r}
m <- 11000 
sd <- 1960000 **(1/2)
round(1-pnorm(8340, m, sd), 4)
```

@@

@@

@@

```{r}
m <- 6.13 
sd <- 0.06
p <- 7/100
round(qnorm(p, m, sd), 3)
round(qnorm(p, m, sd, lower.tail = FALSE), 3)
```

@@

@@

@@

@@

@@

@@

Lower Bound:
Upper Bound:

>>>>

**0.9458**

```{r}
m <- 1300 
sd <- 40000**(1/2)
x <- 979
z <- (x-m)/sd
round(1-pnorm(z),4)
```

@@

**0.9713**

```{r}
m <- 11000 
sd <- 1960000 **(1/2)
x <- 8340
z <- (x-m)/sd
round(1-pnorm(z),4)
round(1-pnorm(x, m, sd), 4)
```

@@

**0.1109**

@@

**589**

@@

**6.04 and 6.22 cm**

```{r}
m <- 6.13 
sd <- 0.06
p <- 7/100
round(qnorm(p, m, sd), 2)
round(qnorm(p, m, sd, lower.tail = FALSE), 2)
```

@@

**71 and 80**

@@

**21.9**

@@

```{r}

```

@@

$$ Z = \frac{(X-\mu)}{\sigma}=\frac{(48.83-48)}{7}=0.1185714$$

Looking it up in a Z table the area under the curve (to the left) is 0.5478.  Since we are looking for the area greater than 48.83 we take 1 - 0.5478 = **0.4528**

```{r}
z <- (48.83-48)/7
round(1 - pnorm(z),4)
```

@@

$$ Z = \frac{(X-\mu)}{\sigma}=\frac{(93.54-91)}{10}=0.254$$

**0.4388**

```{r}
m <- 91
x <- 92.54
sd <- 10
z <- (x-m)/sd
round(pnorm(z, lower.tail = FALSE), 4)
```

@@

Lower Bound:

Upper Bound:
